### 2013-04-18 drafts/grammar/grammar.tex

\renewcommand{\grammarlabel}[2]{#1 #2}

@@

Here each task $t_i$ is interpreted as a noisy version of the
underlying program $e_i$, and there is an associated likelihood
function $p_{t|e}(t|e) \propto f(t(e)) $ where $f$ is a monotonically
decreasing function. Given a task-specific loss function $t(\cdot)$, a
natural likelihood is $p_{t|e}(t|e) \propto \exp^{-t(e)}$. A set of
programs $\{e_i\}$ is drawn from a grammar $G$, which functions as the
subroutine library. Our prior expectations about $G$ are encoded in
$\theta$ via the distribution $p_{G|\theta}$.

The goal of the learner is the find the library $G$ and programs
$\{e_i\}$ that maximize $P(\{e_i\}, G | \{t_i\}, \theta)$. That is,

\begin{align}
G^*, \{e^*_i\} &= \argmax_{G, \{e_i\} }
   P(\{e_i\}, G | \{t_i\}, \theta)\\
&= \argmax_{G, \{e_i\} } P(\{t_i\} | \{e_i\})
  P(\{e_i\} | G) P(G | \theta)\\
&= \argmax_{G, \{e_i\} }
  \sum_i \left( 
  \log{p_{t|e}(t_i|e_i)}+ 
  \log{p_{e|G}(e_i|G)}
  \right ) +
  \log{p_{G|\theta}(G|\theta)}
\label{eq:objective}
\end{align}

The main difficulty in this optimization is that finding any candidate
program $e_i$ that provides a significant value for the first term is
difficult. If we new $G$, we could sample programs from it as a way to
guide searching over the $e_i$. This suggests the following iterative
heuristic search algorithm. At iteration $j$, let $G^{(j)}$ be the
current best value of $G$.

>>>>

\renewcommand{\grammarlabel}[2]{#1 #2}
\renewcommand{\given}{\, | \,}

@@

Here each task $t_i$ is interpreted as a noisy version of the
underlying program $e_i$, and there is an associated likelihood
function $p_{t\given e}(t \given e) \propto f(t(e)) $ where $f$ is a monotonically
decreasing function. Given a task-specific loss function $t(\cdot)$, a
natural likelihood is $p_{t \given e}(t \given e) \propto \exp^{-t(e)}$. A set of
programs $\{e_i\}$ is drawn from a grammar $G$, which functions as the
subroutine library. Our prior expectations about $G$ are encoded in
$\theta$ via the distribution $p_{G \given \theta}$.

The goal of the learner is the find the library $G$ and programs
$\{e_i\}$ that maximize $P(\{e_i\}, G \given  \{t_i\}, \theta)$. That is,

\begin{align}
G^*, \{e^*_i\} &= \argmax_{G, \{e_i\} }
   P(\{e_i\}, G \given  \{t_i\}, \theta)\\
&= \argmax_{G, \{e_i\} }  P(\{t_i\} \given \{e_i\}) \;
  P(\{e_i\} \given G) \; P(G \given \theta)\\
&= \argmax_{G, \{e_i\} }
  \sum_i \left( 
  \log{p_{t\given e}\;(t_i \given e_i)}+ 
  \log{p_{e \given G}(e_i \given G)}
  \right ) +
  \log{p_{G \given \theta}\; (G \given \theta)}
\label{eq:objective}
\end{align}

The main difficulty in this optimization is that finding any candidate
program $e_i$ that provides a significant value for the first term is
difficult. If we knew $G$, we could sample programs from it as a way to
guide the search over the $e_i$. This suggests the following iterative
heuristic search algorithm. At iteration $j$, let $G^{(j)}$ be the
current best value of $G$.
